### 2012-12-12 inst/examples/may79-example.Rmd
Exploring GP behavior and origin of deviations

```{r}
x_grid = seq(0, 1.5 * K, length=101)
T <- 40
sigma_g <- 0.3
x <- numeric(T)
x[1] <- 1
```

@@

Noise function, profit function
```{r}
z_g <- function(sigma_g) rlnorm(1, 0, sigma_g) #1+(2*runif(1, 0,  1)-1)*sigma_g #
profit <- profit_harvest(1,0,0)
```

@@

GP Solution

```{r}
matrices_gp <- gp_transition_matrix(Ef, sqrt(V), x_grid, h_grid)
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```

>>>>

```{r}
x_grid = seq(0, 1.5 * K, length=101)
T <- 40
sigma_g <- 0.6
x <- numeric(T)
x[1] <- 1
```

@@

Noise function, profit function
```{r}
z_g <- function(sigma_g) rlnorm(1, 0, sigma_g) #1+(2*runif(1, 0,  1)-1)*sigma_g #
#profit <- profit_harvest(1,0,0)

profit = function(x,h) pmin(x, h)
```

@@

## Understanding the GP Solution

```{r}
h <- x_grid[1]
X <- numeric(length(x_grid))
X[18] = 1
S <- Ef-h
 F_ <- t(sapply(1:length(S), function(i){
      if(S[i]>0) {
        out <- dnorm(x_grid, S[i], sqrt(V[i]))
#        negatives <- sum(dnorm(seq(-K,0, length=50), S[i], sqrt(V[i])))
#        out[1] <- out[1] + negatives
        out <- out/sum(out)
      } else {
        out <- numeric(length(x_grid))
        out[1] <- 1
        out
      }
    }))
xt1 <- X %*% F_

xt10 <- xt1
for(s in 1:20)
  xt10 <- xt10 %*% F_

qplot(x_grid, xt1[1,])
```

whereas

```{r}
rownorm <- function(M) t(apply(M, 1, function(x) x/sum(x)))

mu <- sapply(x_grid, f, h, p)
F_true <- t(sapply(mu, function(m){
      if(m>0) {
        out <- dlnorm(x_grid/m, 0, sigma_g)

      } else {
        out <- numeric(length(x_grid))
        out[1] <- 1
        out
      }
    }))
    F_true <- rownorm(F_true)
F_true <- rownorm(F_true)
yt1 <- X %*% F_true

yt10 <- yt1
for(s in 1:10)
  yt10 <- yt10 %*% F_true
qplot(x_grid, yt10[1,])
```

```{r}
transition <- melt(data.frame(x = x_grid, gp = xt1[1,], parametric = yt1[1,]), id="x")
ggplot(transition) + geom_point(aes(x,value, col=variable))
```

```{r}
matrices_gp <- gp_transition_matrix(Ef, V, x_grid, h_grid)
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```

```{r}
F <- matrices_gp
Tmax <- 20
    n_x <- length(x_grid)
    n_h <- length(h_grid)
    D <- matrix(NA, nrow=n_x, ncol=Tmax)  
    P <-  outer(x_grid, h_grid, profit)   
    V <- P
    for(t in 1:Tmax){
      D[,(Tmax-t+1)] <- apply(V, 1, which.max) 
      v_t <- apply(V, 1, max) # vector of current values 
      V <- sapply(1:n_h, function(j) # updated value matrix
        P[,j] + (1-delta) * F[[j]] %*% v_t)
    }
```
